Innovative Technologies for and Observational Studies of Star and Planet Formation

### 2014-08-20 chGratingProcess/chapter-gratingprocess.tex
organize the chapters into folders with their figures

\subfloat[Projected photoresist interference curve]{\psfig{file=S1800interference,height=2.75in,width=3.25in}}
\\
\subfloat[Center to edge variation assuming the projected interference]{\psfig{file=projectedC2Evariation,height=2.75in,width=3.25in}}
\caption[Projected photoresist interference]{The projected photoresist interference assuming mercury G-line wavelength exposure.  The inset shows a blow-up of the thickness range surrounding the thickness of our photoresist, 800 nm.  The thickness of our resist ranges from 807 nm at center to 800 nm at edge, which corresponds to a projected critical exposure difference of 82 mJ/cm$^2$ to 90 mJ/cm$^2$.}
\label{fig:S1800interference}
\end{center}
\end{figure}

@@

\begin{figure}[h!] 
\begin{center}
\psfig{file=UV_spec_abs,height=3.0in,width=3.50in}
\caption[UV absorption and lamp spectrum]{The absorbed power density as a function of wavelength.  This curve is the product of the lamp wavelength and the absorption of the S1800 photoresist.  See the text for the assumptions and extrapolations.  The line at 435 nm is the mercury G-line.  It is clear that the other lines contribute strongly to the delivered dose of the S1800 photoresist.  These other peaks should smear out the interference curves shown Figure \ref{fig:S1800interference}.}
\label{fig:UVabsSPEC}
\end{center}
\end{figure}

@@

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=UV_expos_graphic2.pdf,height=4.5in,width=4in}
\caption[Schematic of our UV exposure system]{Schematic of our UV exposure system.  The UV exposure system operates by moving the mask-substrate unit beneath a stationary UV light source.  The key components of the system are labeled.  The ultra stable UV lamp (a) is fiber fed to a collimating mirror, before passing through a 1'' $\times$ 6'' slit (b) with its long axis perpendicular to the direction of motion of the car (c).  A 632 nm laser beam (d) illuminates a 1'' diameter beam on the mask-substrate unit to aid in minimizing Newton's rings fringes from poor contact.  The beam is viewed on a white card (e).  A computer controlled motor (f,g) controls the delivered exposure dose by defining the rate of motion and number of passes for the car.}
\label{fig:uvsys}
\end{center}
\end{figure}

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=UV_expos_graphic1.pdf,height=4.5in,width=4in}
\caption[Schematic of our former UV exposure system]{Schematic of our setup for the UV exposure system before 2010.  The key difference of the previous exposure system and the current system is the strategy for illumination, specifically collimation.  In the old system we simply had the light guide directed downward from the top of the tower, whereas in the new system we have a mirror at the top of the tower to receive the divergent beam from the light guide and subsequently collimate the beam toward the slit.}
\label{fig:uvsys}
\end{center}
\end{figure}

@@

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=dose2clear.pdf,height=4in,width=5.5in}
\caption[S1800 photoresist contrast curve]{S1800 photoresist contrast curve.  The red points are digitized values from Figure 7 of the Shipley S1800 series photoresist guide.  The $x-$ axis is the log of the exposure dose in mJ/cm$^2$.  The blue points are UT lab-measured values in number of passes plus a constant $x$ offset to match up with the scale on the Shipley measured values.  We know from the Shipley report that their values are for S1813 resist thickness 1230 nm, whereas our S1805 resist thickness is 700 nm, so we do not expect the dose to clear to be equal for these two different cases.  In fact, Figure 4 in the Shipley product guide shows that the dose to clear, $E_0$, can vary by 50\% for an 8\% change in resist thickness.}
\label{fig:dose2clear}
\end{center}
\end{figure}

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=dose2clear2.pdf,height=4in,width=5.5in}
\caption[Experimental photoresist contrast curve]{Photoresist contrast curve in units of number of passes on a linear scale.}
\label{fig:dose2clear2}
\end{center}
\end{figure}

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=IMG_3285.jpg,height=5in,width=4in}
\caption[Photo of experimental wafer]{Photo of the wafer used to make figures \ref{fig:dose2clear2} and \ref{fig:dose2clear}.  The large scale non-uniformities are apparent at the region near the critical dose.}
\label{fig:dose2clearphoto}
\end{center}
\end{figure}

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=3Dzoomw20120926.pdf,height=5in,width=6.25in}
\caption[Zygo interferometry of experimental wafer]{Zygo interferometry at maximum zoom.  The target is the wafer shown in the photo in Figure \ref{fig:dose2clearphoto}, centered around the region near the critical dose.  The 3D map shows fine spatial structure that is barely perceptible.  The steps are approximately 5 mm wide.  }
\label{fig:3dZYGOresist}
\end{center}
\end{figure}

@@

\begin{figure}[h!] 
\begin{center}
\subfloat[Schematic of the Wafer and UV slit motion]{\ \psfig{file=UV_slit,height=2in,width=3in}}
\\
\subfloat[Vibration effect on position and dwell time]{\ \psfig{file=UV_vibrations,height=3in,width=6in}}
\caption[Motor vibrations schematic]{The effect of vibrations is to produce periodic exposure dose as a function of position.  The period is about 210 $\mu$m, which is equal to the observed frequency.}
\label{fig:uvvibs}
\end{center}
\end{figure}

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=zeiss_period,height=4.6in,width=6in}
\caption[High frequency structure in the photo resist]{High frequency structure in the photo resist color difference as probed by optical microscopy.  The Zeiss microscope at 5x shows a field of view a bit over 1.2 mm wide, showing subtle periodic waves in the resist thickness.  The period is in the range of 200-240 $\mu$m.  }
\label{fig:zeissfreq}
\end{center}
\end{figure}

@@

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=resonantmotor.pdf,height=2.5in,width=3.5in}
\caption[Motor vibration amplitude]{RMS vibration amplitude as a function of driving frequency of the motor.}
\label{fig:resonantmotor}
\end{center}
\end{figure}

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=freqresponse.pdf,height=2.5in,width=3.5in}
\caption[Motor vibration frequency]{Peak frequency of vibration as a function of driving frequency.  The power is almost entirely in the $x-$axis, which is the direction of motion of the car.}
\label{fig:freqresponse}
\end{center}
\end{figure}

>>>>

\subfloat[Projected photoresist interference curve]{\psfig{file=chGratingProcess/S1800interference.pdf,height=2.75in,width=3.25in}}
\\
\subfloat[Center to edge variation assuming the projected interference]{\psfig{file=chGratingProcess/projectedC2Evariation.pdf,height=2.75in,width=3.25in}}
\caption[Projected photoresist interference]{The projected photoresist interference assuming mercury G-line wavelength exposure.  The inset shows a blow-up of the thickness range surrounding the thickness of our photoresist, 800 nm.  The thickness of our resist ranges from 807 nm at center to 800 nm at edge, which corresponds to a projected critical exposure difference of 82 mJ/cm$^2$ to 90 mJ/cm$^2$.}
\label{fig:S1800interference}
\end{center}
\end{figure}

@@

\begin{figure}[h!] 
\begin{center}
\psfig{file=chGratingProcess/UV_spec_abs.pdf,height=3.0in,width=3.50in}
\caption[UV absorption and lamp spectrum]{The absorbed power density as a function of wavelength.  This curve is the product of the lamp wavelength and the absorption of the S1800 photoresist.  See the text for the assumptions and extrapolations.  The line at 435 nm is the mercury G-line.  It is clear that the other lines contribute strongly to the delivered dose of the S1800 photoresist.  These other peaks should smear out the interference curves shown Figure \ref{fig:S1800interference}.}
\label{fig:UVabsSPEC}
\end{center}
\end{figure}

@@

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=chGratingProcess/UV_expos_graphic2.pdf,height=4.5in,width=4in}
\caption[Schematic of our UV exposure system]{Schematic of our UV exposure system.  The UV exposure system operates by moving the mask-substrate unit beneath a stationary UV light source.  The key components of the system are labeled.  The ultra stable UV lamp (a) is fiber fed to a collimating mirror, before passing through a 1'' $\times$ 6'' slit (b) with its long axis perpendicular to the direction of motion of the car (c).  A 632 nm laser beam (d) illuminates a 1'' diameter beam on the mask-substrate unit to aid in minimizing Newton's rings fringes from poor contact.  The beam is viewed on a white card (e).  A computer controlled motor (f,g) controls the delivered exposure dose by defining the rate of motion and number of passes for the car.}
\label{fig:uvsys}
\end{center}
\end{figure}

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=chGratingProcess/UV_expos_graphic1.pdf,height=4.5in,width=4in}
\caption[Schematic of our former UV exposure system]{Schematic of our setup for the UV exposure system before 2010.  The key difference of the previous exposure system and the current system is the strategy for illumination, specifically collimation.  In the old system we simply had the light guide directed downward from the top of the tower, whereas in the new system we have a mirror at the top of the tower to receive the divergent beam from the light guide and subsequently collimate the beam toward the slit.}
\label{fig:uvsys}
\end{center}
\end{figure}

@@

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=chGratingProcess/dose2clear.pdf,height=4in,width=5.5in}
\caption[S1800 photoresist contrast curve]{S1800 photoresist contrast curve.  The red points are digitized values from Figure 7 of the Shipley S1800 series photoresist guide.  The $x-$ axis is the log of the exposure dose in mJ/cm$^2$.  The blue points are UT lab-measured values in number of passes plus a constant $x$ offset to match up with the scale on the Shipley measured values.  We know from the Shipley report that their values are for S1813 resist thickness 1230 nm, whereas our S1805 resist thickness is 700 nm, so we do not expect the dose to clear to be equal for these two different cases.  In fact, Figure 4 in the Shipley product guide shows that the dose to clear, $E_0$, can vary by 50\% for an 8\% change in resist thickness.}
\label{fig:dose2clear}
\end{center}
\end{figure}

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=chGratingProcess/dose2clear2.pdf,height=4in,width=5.5in}
\caption[Experimental photoresist contrast curve]{Photoresist contrast curve in units of number of passes on a linear scale.}
\label{fig:dose2clear2}
\end{center}
\end{figure}

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=chGratingProcess/IMG_3285.jpg,height=5in,width=4in}
\caption[Photo of experimental wafer]{Photo of the wafer used to make figures \ref{fig:dose2clear2} and \ref{fig:dose2clear}.  The large scale non-uniformities are apparent at the region near the critical dose.}
\label{fig:dose2clearphoto}
\end{center}
\end{figure}

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=chGratingProcess/3Dzoomw20120926.pdf,height=5in,width=6.25in}
\caption[Zygo interferometry of experimental wafer]{Zygo interferometry at maximum zoom.  The target is the wafer shown in the photo in Figure \ref{fig:dose2clearphoto}, centered around the region near the critical dose.  The 3D map shows fine spatial structure that is barely perceptible.  The steps are approximately 5 mm wide.  }
\label{fig:3dZYGOresist}
\end{center}
\end{figure}

@@

\begin{figure}[h!] 
\begin{center}
\subfloat[Schematic of the Wafer and UV slit motion]{\ \psfig{file=chGratingProcess/UV_slit.pdf,height=2in,width=3in}}
\\
\subfloat[Vibration effect on position and dwell time]{\ \psfig{file=chGratingProcess/UV_vibrations.pdf,height=3in,width=6in}}
\caption[Motor vibrations schematic]{The effect of vibrations is to produce periodic exposure dose as a function of position.  The period is about 210 $\mu$m, which is equal to the observed frequency.}
\label{fig:uvvibs}
\end{center}
\end{figure}

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=chGratingProcess/zeiss_period.pdf,height=4.6in,width=6in}
\caption[High frequency structure in the photo resist]{High frequency structure in the photo resist color difference as probed by optical microscopy.  The Zeiss microscope at 5x shows a field of view a bit over 1.2 mm wide, showing subtle periodic waves in the resist thickness.  The period is in the range of 200-240 $\mu$m.  }
\label{fig:zeissfreq}
\end{center}
\end{figure}

@@

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=chGratingProcess/resonantmotor.pdf,height=2.5in,width=3.5in}
\caption[Motor vibration amplitude]{RMS vibration amplitude as a function of driving frequency of the motor.}
\label{fig:resonantmotor}
\end{center}
\end{figure}

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=chGratingProcess/freqresponse.pdf,height=2.5in,width=3.5in}
\caption[Motor vibration frequency]{Peak frequency of vibration as a function of driving frequency.  The power is almost entirely in the $x-$axis, which is the direction of motion of the car.}
\label{fig:freqresponse}
\end{center}
\end{figure}
